Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study

### 2021-04-08 csmc_mume_2020/paper/JCMS_2021/paper.tex
Add Carmine's changes

% first the title is needed
\title{A Study on Neural Models for Target-Based Computer-Assisted Musical Orchestration}

@@

\begin{abstract}
In this paper we will perform a preliminary exploration on how neural networks can be used for the task of target-based computer-assisted musical orchestration. We will show how it is possible to model this  musical problem as a classification task and we will propose two deep learning models. We will show, first, how they perform as classifiers for musical instrument recognition by comparing them with specific baselines. We will then show how they perform, both qualitatively and quantitatively, in the task of computer-assisted orchestration by comparing them with state-of-the-art systems. Finally, we will highlight benefits and problems of neural approaches for assisted orchestration and we will propose possible future steps.

@@

This paper is an extended version of a paper by the same title in \textit{The 2020 Joint Conference on AI Music Creativity} \cite{Cella2020c}. This version includes additional figures and extended information on our baseline testing and orchestration process, among other additions. The codebase for this paper can be found at \url{https://github.com/dzluke/DeepOrchestration} and you can listen to audio examples at \url{https://dzluke.github.io/DeepOrchestration/}.

>>>>

% first the title is needed
\title{Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study}

@@

\begin{abstract}
In this paper we will perform a preliminary exploration on how neural networks can be used for the task of target-based computer-assisted musical orchestration. We will show how it is possible to model this  musical problem as a classification task and we will propose two deep learning models. We will show, first, how they perform as classifiers for musical instrument recognition by comparing them with specific baselines. We will then show how they perform, both qualitatively and quantitatively, in the task of computer-assisted orchestration by comparing them with state-of-the-art systems. Finally, we will highlight benefits and problems of neural approaches for assisted orchestration and we will propose possible future steps. This paper is an extended version of the paper ``A Study on Neural Models for Target-Based Computer-Assisted Musical Orchestration" published in the proceedings of \textit{The 2020 Joint Conference on AI Music Creativity}.

@@

\sloppypar{The codebase for this paper can be found at \url{https://github.com/dzluke/DeepOrchestration} and you can listen to audio examples at \url{https://dzluke.github.io/DeepOrchestration/}.}
